---
title: "Analyse data - shared room, outer London"
---

# import packages & function

```{r}
library(dplyr)
library(quanteda)
library(topicmodels)
get_dfm <- readRDS("function_get_dfm.rds")
```

# import data

```{r}
shared_outer_df <- readRDS("full_shared_outer.rds")
```

# get dfm

```{r}
shared_outer_dfm_trimmed <- get_dfm(shared_outer_df)
```

# fit model (k = 30)

```{r}
shared_outer_lda_30 <- LDA(shared_outer_dfm_trimmed, 
                           k = 30, 
                           method = "Gibbs", 
                           control = list(seed = 6, verbose = 25, burnin = 100, iter = 500))
```

# save & import model

```{r}
# saveRDS(shared_outer_lda_30, "shared_outer_lda_30.rds")

shared_outer_lda_30 <- readRDS("shared_outer_lda_30.rds")
```

# descriptive keywords for each topic

```{r}
shared_outer_parameters <- as.data.frame(get_terms(shared_outer_lda_30, 20), stringsAsFactors = FALSE)
```

get segments:
* price value (topic 3, 20, 26, 27)
* location - practical demand (topic 15, 25, 30)
* home benefits (topic 8, 16, 22)
* enjoyment (topic 4, 7, 9, 12, 14, 17, 19, 23, 24, 29)
* social interaction (topic 6)
* novelty (topic 5)

* home benefits & enjoyment overlap (topic 13)
* location - practical demand & experiential demand overlap (topic 10)

redundant topics: 1, 2, 11, 18, 21, 28

# topic for each review

```{r}
shared_outer_topic <- get_topics(shared_outer_lda_30, 1)
shared_outer_topic <- data.frame(review_id = as.integer(names(shared_outer_topic)), topic = shared_outer_topic, stringsAsFactors = FALSE)
rownames(shared_outer_topic) <- seq(1, nrow(shared_outer_topic), by = 1)
```

# sample review for each segment

```{r}
shared_outer_df[shared_outer_df$id == sample(shared_outer_topic$review_id[shared_outer_topic$topic == 29], 1), 5]
```

# relative segment size/importance

```{r}
shared_outer_topic_distribution <- as.data.frame(shared_outer_lda_30@gamma, stringsAsFactors = FALSE)
colnames(shared_outer_topic_distribution) <- colnames(shared_outer_parameters)
shared_outer_topic_distribution <- data.frame(shared_outer_topic_distribution, 
                                              price_value = rowSums(shared_outer_topic_distribution[ , c(3, 20, 26, 27)]), 
                                              location_practical_demand = rowSums(shared_outer_topic_distribution[ , c(15, 25, 30)]), 
                                              home_benefit = rowSums(shared_outer_topic_distribution[ , c(8, 16, 22)]), 
                                              enjoyment = rowSums(shared_outer_topic_distribution[ , c(4, 7, 9, 12, 14, 17, 19, 23, 24, 29)]), 
                                              review_id = shared_outer_topic$review_id, 
                                              stringsAsFactors = FALSE)

# price value
sum(shared_outer_topic$topic %in% c(3, 20, 26, 27))
mean(shared_outer_topic_distribution$price_value)
# location - practical demand
sum(shared_outer_topic$topic %in% c(15, 25, 30))
mean(shared_outer_topic_distribution$location_practical_demand)
# home benefits
sum(shared_outer_topic$topic %in% c(8, 16, 22))
mean(shared_outer_topic_distribution$home_benefit)
# enjoyment
sum(shared_outer_topic$topic %in% c(4, 7, 9, 12, 14, 17, 19, 23, 24, 29))
mean(shared_outer_topic_distribution$enjoyment)
# social interaction
sum(shared_outer_topic$topic == 6)
mean(shared_outer_topic_distribution$Topic.6)
# novelty
sum(shared_outer_topic$topic == 5)
mean(shared_outer_topic_distribution$Topic.5)
# home benefits & enjoyment overlap
sum(shared_outer_topic$topic == 13)
mean(shared_outer_topic_distribution$Topic.13)
# location - practical demand & experiential demand overlap
sum(shared_outer_topic$topic == 10)
mean(shared_outer_topic_distribution$Topic.10)
```

# change in segment size/importance over years

```{r}
shared_outer_topic_distribution <- left_join(shared_outer_topic_distribution, 
                                             shared_outer_df[ , c(2, 3)], 
                                             by = c("review_id" = "id"))
shared_outer_topic_distribution$year <- as.integer(format(shared_outer_topic_distribution$date, "%Y"))
shared_outer_topic_distribution$month <- as.integer(format(shared_outer_topic_distribution$date, "%m"))

segment_size_by_year <- aggregate(shared_outer_topic_distribution[ , c(31, 32, 33, 34, 6, 5, 13, 10)], by = list(year = shared_outer_topic_distribution$year), FUN = mean)
segment_size_by_month <- aggregate(shared_outer_topic_distribution[ , c(31, 32, 33, 34, 6, 5, 13, 10)], by = list(month = shared_outer_topic_distribution$month), FUN = mean)

plot(segment_size_by_year$year, 
     segment_size_by_year$price_value, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: price value")
plot(segment_size_by_year$year, 
     segment_size_by_year$location_practical_demand, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: location - practical demand")
plot(segment_size_by_year$year, 
     segment_size_by_year$home_benefit, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: home benefits")
plot(segment_size_by_year$year, 
     segment_size_by_year$enjoyment, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: enjoyment")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.6, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: social interaction")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.5, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: novelty")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.13, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: home benefits & enjoyment")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.10, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: location - practical & experiential demand")
```

# seasonal variation in segment size/importance

```{r}
plot(segment_size_by_month$month, 
     segment_size_by_month$price_value, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: price value")
plot(segment_size_by_month$month, 
     segment_size_by_month$location_practical_demand, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: location - practical demand")
plot(segment_size_by_month$month, 
     segment_size_by_month$home_benefit, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: home benefits")
plot(segment_size_by_month$month, 
     segment_size_by_month$enjoyment, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: enjoyment")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.6, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: social interaction")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.5, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: novelty")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.13, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: home benefits & enjoyment")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.10, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: location - practical & experiential demand")
```

# validation of additional segments

```{r}
# create dictionary

dict <- dictionary(list(sustainability = c("environment.*", "philosoph.*", "material", "materials", "develop.*", "support.*", "economy", "sustainab.*", "resource.*")))

# find freqneucy

shared_outer_dfm_validate <- dfm_lookup(shared_outer_dfm_trimmed, 
                                        dictionary = dict, 
                                        valuetype = "regex", 
                                        case_insensitive = TRUE, 
                                        exclusive = FALSE, 
                                        capkeys = TRUE)

# convert to proportion percentage within review

shared_outer_dfm_validate <- dfm_weight(shared_outer_dfm_validate, 
                                        scheme = "prop")
shared_outer_dfm_validate <- shared_outer_dfm_validate[, "SUSTAINABILITY"]

# get average proportion percentage over all reviews for each potential segment
colMeans(shared_outer_dfm_validate)
```