---
title: "Analyse data - private room, outer London"
---

# import packages & function

```{r}
library(dplyr)
library(quanteda)
library(topicmodels)
get_dfm <- readRDS("function_get_dfm.rds")
```

# import data

```{r}
private_outer_df <- readRDS("full_private_outer.rds")
```

# get dfm

```{r}
private_outer_dfm_trimmed <- get_dfm(private_outer_df)
```

# fit model (k = 30)

```{r}
private_outer_lda_30 <- LDA(private_outer_dfm_trimmed, 
                            k = 30, 
                            method = "Gibbs", 
                            control = list(seed = 2, verbose = 25, burnin = 100, iter = 500))
```

# save & import model

```{r}
# saveRDS(private_outer_lda_30, "private_outer_lda_30.rds")

private_outer_lda_30 <- readRDS("private_outer_lda_30.rds")
```

# descriptive keywords for each topic

```{r}
private_outer_parameters <- as.data.frame(get_terms(private_outer_lda_30, 20), stringsAsFactors = FALSE)
```

get segments:
* price value (topic 13)
* location - practical demand (topic 7, 16, 18, 22)
* home benefits (topic 8, 21, 24, 27, 28, 30)
* enjoyment (topic 6, 9, 10, 12, 15, 23, 25, 29)
* novelty (topic 1)

* home benefits & enjoyment overlap (topic 2, 5, 11, 19)
* location - practical demand & experiential demand overlap (topic 26)

redundant topics: 3, 4, 14, 17, 20

# topic for each review

```{r}
private_outer_topic <- get_topics(private_outer_lda_30, 1)
private_outer_topic <- data.frame(review_id = as.integer(names(private_outer_topic)), topic = private_outer_topic, stringsAsFactors = FALSE)
rownames(private_outer_topic) <- seq(1, nrow(private_outer_topic), by = 1)
```

# sample review for each segment

```{r}
private_outer_df[private_outer_df$id == sample(private_outer_topic$review_id[private_outer_topic$topic == 28], 1), 5]
```

# relative segment size/importance

```{r}
private_outer_topic_distribution <- as.data.frame(private_outer_lda_30@gamma, stringsAsFactors = FALSE)
colnames(private_outer_topic_distribution) <- colnames(private_outer_parameters)
private_outer_topic_distribution <- data.frame(private_outer_topic_distribution, 
                                               location_practical_demand = rowSums(private_outer_topic_distribution[ , c(7, 16, 18, 22)]), 
                                               home_benefit = rowSums(private_outer_topic_distribution[ , c(8, 21, 24, 27, 28, 30)]), 
                                               enjoyment = rowSums(private_outer_topic_distribution[ , c(6, 9, 10, 12, 15, 23, 25, 29)]), 
                                               hb_enjoy = rowSums(private_outer_topic_distribution[ , c(2, 5, 11, 19)]), 
                                               review_id = private_outer_topic$review_id, 
                                               stringsAsFactors = FALSE)

# price value
sum(private_outer_topic$topic == 13)
mean(private_outer_topic_distribution$Topic.13)
# location - practical demand
sum(private_outer_topic$topic %in% c(7, 16, 18, 22))
mean(private_outer_topic_distribution$location_practical_demand)
# home benefits
sum(private_outer_topic$topic %in% c(8, 21, 24, 27, 28, 30))
mean(private_outer_topic_distribution$home_benefit)
# enjoyment
sum(private_outer_topic$topic %in% c(6, 9, 10, 12, 15, 23, 25, 29))
mean(private_outer_topic_distribution$enjoyment)
# novelty
sum(private_outer_topic$topic == 1)
mean(private_outer_topic_distribution$Topic.1)
# home benefits & enjoyment overlap
sum(private_outer_topic$topic %in% c(2, 5, 11, 19))
mean(private_outer_topic_distribution$hb_enjoy)
# location - practical demand & experiential demand overlap
sum(private_outer_topic$topic == 26)
mean(private_outer_topic_distribution$Topic.26)
```

# change in segment size/importance over years

```{r}
private_outer_topic_distribution <- left_join(private_outer_topic_distribution, 
                                              private_outer_df[ , c(2, 3)], 
                                              by = c("review_id" = "id"))
private_outer_topic_distribution$year <- as.integer(format(private_outer_topic_distribution$date, "%Y"))
private_outer_topic_distribution$month <- as.integer(format(private_outer_topic_distribution$date, "%m"))

segment_size_by_year <- aggregate(private_outer_topic_distribution[ , c(13, 31, 32, 33, 1, 34, 26)], by = list(year = private_outer_topic_distribution$year), FUN = mean)
segment_size_by_month <- aggregate(private_outer_topic_distribution[ , c(13, 31, 32, 33, 1, 34, 26)], by = list(month = private_outer_topic_distribution$month), FUN = mean)

plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.13, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: price value")
plot(segment_size_by_year$year, 
     segment_size_by_year$location_practical_demand, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: location - practical demand")
plot(segment_size_by_year$year, 
     segment_size_by_year$home_benefit, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: home benefits")
plot(segment_size_by_year$year, 
     segment_size_by_year$enjoyment, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: enjoyment")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.1, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: novelty")
plot(segment_size_by_year$year, 
     segment_size_by_year$hb_enjoy, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: home benefits & enjoyment")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.26, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: location - practical & experiential demand")
```

# seasonal variation in segment size/importance

```{r}
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.13, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: price value")
plot(segment_size_by_month$month, 
     segment_size_by_month$location_practical_demand, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: location - practical demand")
plot(segment_size_by_month$month, 
     segment_size_by_month$home_benefit, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: home benefits")
plot(segment_size_by_month$month, 
     segment_size_by_month$enjoyment, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: enjoyment")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.1, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: novelty")
plot(segment_size_by_month$month, 
     segment_size_by_month$hb_enjoy, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: home benefits & enjoyment")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.26, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: location - practical & experiential demand")
```

# validation of additional segments

```{r}
# create dictionary

dict <- dictionary(list(social_interaction = c("social.*", "shar.*", "insider.*", "intimate.*", "learn.*", "new", "cool", "young", "interesting", "fun", "roommate.*"), 
                        sustainability = c("environment.*", "philosoph.*", "material", "materials", "develop.*", "support.*", "economy", "sustainab.*", "resource.*")))

# find freqneucy

private_outer_dfm_validate <- dfm_lookup(private_outer_dfm_trimmed, 
                                         dictionary = dict, 
                                         valuetype = "regex", 
                                         case_insensitive = TRUE, 
                                         exclusive = FALSE, 
                                         capkeys = TRUE)

# convert to proportion percentage within review

private_outer_dfm_validate <- dfm_weight(private_outer_dfm_validate, 
                                         scheme = "prop")
private_outer_dfm_validate <- private_outer_dfm_validate[, c("SOCIAL_INTERACTION", "SUSTAINABILITY")]

# get average proportion percentage over all reviews for each potential segment
colMeans(private_outer_dfm_validate)
```