---
title: "Analyse data - entire home, outer London"
---

# import packages & function

```{r}
library(dplyr)
library(quanteda)
library(topicmodels)
get_dfm <- readRDS("function_get_dfm.rds")
```

# import data

```{r}
entire_outer_df <- readRDS("full_entire_outer.rds")
```

# get dfm

```{r}
entire_outer_dfm_trimmed <- get_dfm(entire_outer_df)
```

# fit model (k = 30)

```{r}
entire_outer_lda_30 <- LDA(entire_outer_dfm_trimmed, 
                           k = 30, 
                           method = "Gibbs", 
                           control = list(seed = 4, verbose = 25, burnin = 100, iter = 500))
```

# save & import model

```{r}
# saveRDS(entire_outer_lda_30, "entire_outer_lda_30.rds")

entire_outer_lda_30 <- readRDS("entire_outer_lda_30.rds")
```

# descriptive keywords for each topic

```{r}
entire_outer_parameters <- as.data.frame(get_terms(entire_outer_lda_30, 20), stringsAsFactors = FALSE)
```

get segments:
* price value (topic 4)
* location - practical demand (topic 9, 14, 16, 17, 28)
* home benefits (topic 13, 24, 25, 29)
* enjoyment (topic 5, 6, 7, 8, 11, 18, 19, 20, 21, 22, 27)
* location - experiential demand (topic 15, 26)
* novelty (topic 1)

* enjoyment & location - experiential demand overlap (topic 3) 

redundant topics: 2, 10, 12, 23, 30

# topic for each review

```{r}
entire_outer_topic <- get_topics(entire_outer_lda_30, 1)
entire_outer_topic <- data.frame(review_id = as.integer(names(entire_outer_topic)), topic = entire_outer_topic, stringsAsFactors = FALSE)
rownames(entire_outer_topic) <- seq(1, nrow(entire_outer_topic), by = 1)
```

# sample review for each segment

```{r}
entire_outer_df[entire_outer_df$id == sample(entire_outer_topic$review_id[entire_outer_topic$topic == 30], 1), 5]
```

# relative segment size/importance

```{r}
entire_outer_topic_distribution <- as.data.frame(entire_outer_lda_30@gamma, stringsAsFactors = FALSE)
colnames(entire_outer_topic_distribution) <- colnames(entire_outer_parameters)
entire_outer_topic_distribution <- data.frame(entire_outer_topic_distribution, 
                                              location_practical_demand = rowSums(entire_outer_topic_distribution[ , c(9, 14, 16, 17, 28)]), 
                                              home_benefit = rowSums(entire_outer_topic_distribution[ , c(13, 24, 25, 29)]), 
                                              enjoyment = rowSums(entire_outer_topic_distribution[ , c(5, 6, 7, 8, 11, 18, 19, 20, 21, 22, 27)]), 
                                              location_experiential_demand = rowSums(entire_outer_topic_distribution[ , c(15, 26)]), 
                                              review_id = entire_outer_topic$review_id, 
                                              stringsAsFactors = FALSE)

# price value
sum(entire_outer_topic$topic == 4)
mean(entire_outer_topic_distribution$Topic.4)
# location - practical demand
sum(entire_outer_topic$topic %in% c(9, 14, 16, 17, 28))
mean(entire_outer_topic_distribution$location_practical_demand)
# home benefits
sum(entire_outer_topic$topic %in% c(13, 24, 25, 29))
mean(entire_outer_topic_distribution$home_benefit)
# enjoyment
sum(entire_outer_topic$topic %in% c(5, 6, 7, 8, 11, 18, 19, 20, 21, 22, 27))
mean(entire_outer_topic_distribution$enjoyment)
# location - experiential demand
sum(entire_outer_topic$topic %in% c(15, 26))
mean(entire_outer_topic_distribution$location_experiential_demand)
# price value
sum(entire_outer_topic$topic == 1)
mean(entire_outer_topic_distribution$Topic.1)
# enjoyment & location - experiential demand overlap
sum(entire_outer_topic$topic == 3)
mean(entire_outer_topic_distribution$Topic.3)
```

# change in segment size/importance over years

```{r}
entire_outer_topic_distribution <- left_join(entire_outer_topic_distribution, 
                                             entire_outer_df[ , c(2, 3)], 
                                             by = c("review_id" = "id"))
entire_outer_topic_distribution$year <- as.integer(format(entire_outer_topic_distribution$date, "%Y"))
entire_outer_topic_distribution$month <- as.integer(format(entire_outer_topic_distribution$date, "%m"))

segment_size_by_year <- aggregate(entire_outer_topic_distribution[ , c(4, 31, 32, 33, 34, 1, 3)], by = list(year = entire_outer_topic_distribution$year), FUN = mean)
segment_size_by_month <- aggregate(entire_outer_topic_distribution[ , c(4, 31, 32, 33, 34, 1, 3)], by = list(month = entire_outer_topic_distribution$month), FUN = mean)

plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.4, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: price value")
plot(segment_size_by_year$year, 
     segment_size_by_year$location_practical_demand, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: location - practical demand")
plot(segment_size_by_year$year, 
     segment_size_by_year$home_benefit, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: home benefits")
plot(segment_size_by_year$year, 
     segment_size_by_year$enjoyment, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: enjoyment")
plot(segment_size_by_year$year, 
     segment_size_by_year$location_experiential_demand, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: location - experiential demand")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.1, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: novelty")
plot(segment_size_by_year$year, 
     segment_size_by_year$Topic.3, 
     type = "l", 
     xlab = "Year", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Change in segment size over years: enjoyment & location - experiential demand")
```

# seasonal variation in segment size/importance

```{r}
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.4, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: price value")
plot(segment_size_by_month$month, 
     segment_size_by_month$location_practical_demand, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: location - practical demand")
plot(segment_size_by_month$month, 
     segment_size_by_month$home_benefit, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: home benefits")
plot(segment_size_by_month$month, 
     segment_size_by_month$enjoyment, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: enjoyment")
plot(segment_size_by_month$month, 
     segment_size_by_month$location_experiential_demand, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: location - experiential demand")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.1, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: novelty")
plot(segment_size_by_month$month, 
     segment_size_by_month$Topic.3, 
     type = "l", 
     xlab = "Month", 
     ylab = "Avg. prob. of reviews about segment",
     main = "Seasonal variation in segment size: enjoyment & location - experiential demand")
```

# validation of additional segments

```{r}
# create dictionary

dict <- dictionary(list(social_interaction = c("social.*", "shar.*", "insider.*", "intimate.*", "learn.*", "new", "cool", "young", "interesting", "fun", "roommate.*"), 
                        sustainability = c("environment.*", "philosoph.*", "material", "materials", "develop.*", "support.*", "economy", "sustainab.*", "resource.*")))

# find freqneucy

entire_outer_dfm_validate <- dfm_lookup(entire_outer_dfm_trimmed, 
                                        dictionary = dict, 
                                        valuetype = "regex", 
                                        case_insensitive = TRUE, 
                                        exclusive = FALSE, 
                                        capkeys = TRUE)

# convert to proportion percentage within review

entire_outer_dfm_validate <- dfm_weight(entire_outer_dfm_validate, 
                                        scheme = "prop")
entire_outer_dfm_validate <- entire_outer_dfm_validate[, c("SOCIAL_INTERACTION", "SUSTAINABILITY")]

# get average proportion percentage over all reviews for each potential segment
colMeans(entire_outer_dfm_validate)
```